\textsf{Are large language models superhuman chemists?}

### 2024-03-28 src/tex/ms.tex
acknowledge sandeep
manual curation table

\subsection{Curation workflow}\label{sec:curation}
For our dataset, we curated questions from existing exams but also programmatically created new questions.
Questions were added via Pull Requests on our GitHub repository and only merged into the corpus after passing manual review (\Cref{fig:curation_workflow}).

@@

\paragraph{Manually curated questions}
Manually curated questions were sourced from various sources, including university exams, textbooks, and question banks. \Cref{tab:manually_sources} provides an overview of the sources of the manually curated questions.

@@

In addition, we thank the OpenBioML.org community and their ChemNLP project team for valuable discussions.
Moreover, we thank Pepe Márquez for discussions and support and Julian Kimmig for feedback on the web app. 
We thank Bastian Rieck for developing the \LaTeX-credit package (\url{https://github.com/Pseudomanifold/latex-credits}).

>>>>

\subsection{Curation workflow}\label{sec:curation}
For our dataset, we curated questions from existing exams or exercise sheets but also programmatically created new questions.
Questions were added via Pull Requests on our GitHub repository and only merged into the corpus after passing manual review (\Cref{fig:curation_workflow}) as well as automated checks (e.g., for compliance with a standardized schema).

@@

\paragraph{Manually curated questions}
Manually curated questions were sourced from various sources, including university exams, exercises, and question banks. \Cref{tab:manually_sources} provides an overview of the sources of the manually curated questions.

@@

In addition, we thank the OpenBioML.org community and their ChemNLP project team for valuable discussions.
Moreover, we thank Pepe Márquez for discussions and support and Julian Kimmig for feedback on the web app. 
In addition, we acknowledge support from Sandeep Kumar with an initial prototype of the web app.
We thank Bastian Rieck for developing the \LaTeX-credit package (\url{https://github.com/Pseudomanifold/latex-credits}).
